### 2008-12-20 talk/ecoop2009/rainbow.tex
Standardize the footnote format.

In addition to virtual instances, the compiler can also handle virtual
containers, namely lists and dictionaries \footnote{(R)Python's dictionaries
  are equivalent to .NET \lstinline{Hashtable}s}.  If the indexing operations
can be evaluated at compile-time (i.e., if the variables holding the indexes
are green), the compiler internally keeps track of the state of the container
and store the items as local variables.

@@

By promoting the class of \lstinline{a} and \lstinline{b}, we tell the JIT
compiler not to generate code until it knows the exact RPython class of both.
Figure \ref{fig:tlc-abs-promotion-1} shows the
code \footnote{\lstinline{switch} is not a legal (R)Python statement, it is
  used here only as a pseudocode example} generated while compiling the usual
\lstinline{abs} function: note that, compared to figure
\ref{fig:tlc-folded-virtualized}, the code stops just before the calls
\lstinline{b.lt(a)}.

>>>>

In addition to virtual instances, the compiler can also handle virtual
containers, namely lists and dictionaries\footnote{(R)Python's dictionaries
  are equivalent to .NET \lstinline{Hashtable}s}.  If the indexing operations
can be evaluated at compile-time (i.e., if the variables holding the indexes
are green), the compiler internally keeps track of the state of the container
and store the items as local variables.

@@

By promoting the class of \lstinline{a} and \lstinline{b}, we tell the JIT
compiler not to generate code until it knows the exact RPython class of both.
Figure \ref{fig:tlc-abs-promotion-1} shows the
code\footnote{\lstinline{switch} is not a legal (R)Python statement, it is
  used here only as a pseudocode example.} generated while compiling the usual
\lstinline{abs} function: note that, compared to figure
\ref{fig:tlc-folded-virtualized}, the code stops just before the call
\lstinline{b.lt(a)}.
